\documentclass{phys151}

\title{Homework 4}
\date{2021 October 11 (Monday)}
\author{}

\begin{document}

\begin{problem}
  Show that the value of \(\phi\) in vacuum at any point is equal to the
  average of \(\phi\) over the surface of \emph{any} sphere centered at that
  point.
  \begin{hint}
    Use Green's theorem with appropriate \(\varphi\) and \(\psi\).
  \end{hint}
\end{problem}

\begin{solution}

\end{solution}

\begin{problem}
  \begin{subproblems}
  \item Find \(\phi\) for a conducting sphere in a uniform electric field
    \(E_0\) using the method of images.
  \item Find the surface charge density on the sphere and show that the
    \emph{total} charge is zero.
  \end{subproblems}
\end{problem}

\begin{solution}

\end{solution}

\begin{problem}
  Consider a hollow conducting \emph{grounded} sphere of radius \(b\) with a
  concentric ring of charge inside it given by
  \[
    \rho(\vec x') = \frac Q {2 \pi a^2} \, \delta(r'-a) \, \delta(\cos \theta').
  \]
  Find \(\phi\) everywhere inside the sphere.
  \begin{hint}
    For this, you need the Dirichlet Green's function \(G_D\) for a region
    bounded by two spheres of radii \(R_1\) and \(R_2\), where \(R_1 < R_2\):
    \[
      G_D(x, x') = 4 \pi \sum_{\ell=0}^\infty \sum_{m=-\ell}^\ell
      \frac
      {Y_{\ell m}^* (\theta', \varphi') Y_{\ell m} (\theta, \varphi)}
      {(2\ell+r) \paren* {1 - \paren* {R_1/R_2}^{2\ell+1}}}
      \paren* {r_<^\ell - \frac {R_1^{2\ell+1}} {r_<^{\ell+1}}}
      \paren* {\frac 1 {r_>^{\ell+1}} - \frac {r_>^\ell} {R_2^{2\ell+1}}}.
    \]
    with \(R_1 \to 0\) and \(R_2 = b\).
  \end{hint}
  Verify the \(b \to \infty\) limit with the result from class.  You may leave
  your answer in the form of an infinite sum.
\end{problem}

\begin{solution}

\end{solution}

\begin{problem}
  Consider a hollow conducting grounded sphere of radius \(b\) with a uniform
  line charge of total charge \(Q\) located on the \(z\)-axis between the north
  and south poles.
  \begin{subproblems}
  \item Show that
    \[
      \rho(x') = \frac Q {2b} \frac 1 {2 \pi r'^2}
      \paren* {\delta(\cos \theta' - 1) + \delta(\cos \theta' + 1)}.
    \]
  \item Find \(\phi\) everywhere inside the sphere.
    \begin{hint}
      For this, you need the Dirichlet Green's function \(G_D\) for a region
      bounded by two spheres of radii \(a\) and \(b\), where \(a<b\):
      \[
        G_D(x, x') = 4 \pi \sum_{\ell=0}^\infty \sum_{m=-\ell}^\ell
        \frac
        {Y_{\ell m}^* (\theta', \varphi') Y_{\ell m} (\theta, \varphi)}
        {(2\ell+r) \paren* {1 - (a/b)^{2\ell+1}}}
        \paren* {r_<^\ell - \frac {a^{2\ell+1}} {r_<^{\ell+1}}}
        \paren* {\frac 1 {r_>^{\ell+1}} - \frac {r_>^\ell} {b^{2\ell+1}}}.
      \]
      You will also need
      \[
        \deriv {} y \brack* {x^y} = x^y \ln x,
        \qquad P_\ell(1) = 1,
        \qquad P_\ell(-1) = (-1)^\ell.
      \]
    \end{hint}
  \item Find the surface charge density on the sphere.
  \end{subproblems}
\end{problem}

\begin{solution}

\end{solution}

\end{document}
